### 2024-02-09 documentation/thesis/thesis_document.tex
more thesis

@@

@@

@@

\hypertarget{hardware-preperation}{%
\section{Hardware preperation}\label{hardware-preperation}}

@@

\hypertarget{configuration-of-the-measurement}{%
\section{Configuration of the
Measurement}\label{configuration-of-the-measurement}}

@@

\hypertarget{custom-algorithm-implementation}{%
\section{Custom Algorithm
Implementation}\label{custom-algorithm-implementation}}

@@

\hypertarget{alternative-filter-algorithm-implementation}{%
\subsection{Alternative Filter Algorithm
Implementation}\label{alternative-filter-algorithm-implementation}}

@@

\hypertarget{execution-of-analysis-pipeline}{%
\section{Execution of Analysis
Pipeline}\label{execution-of-analysis-pipeline}}

@@

@@

>>>>

In the Evaluation \ref{evaluation} chapter, basic characterisation
methods are used to evaluate the sensors listed in
\ref{Implemented_digital_magnetic_field_sensors.csv} with regard to
their sensitivity and other parameters. This is done at this point, as
the components of the readout interface that enable interaction with the
sensors are considered first.

@@

TODO: fix links o evaluation

@@

\hypertarget{hardware-evaluation}{%
\section{Hardware Evaluation}\label{hardware-evaluation}}

\begin{itemize}
\tightlist
\item
  cheap sensors used
\item
  used hardware list
\item
  tested sensor tlv mmc, da diese zum zeitpunkt des tests zur verfüung
  standen
\end{itemize}

\hypertarget{read-noise}{%
\subsection{Read Noise}\label{read-noise}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_noise_measurements.png}
\caption{Sensor evaluation setup for noise measurements
\label{Sensor_evaluation_setup_for_noise_measurements.png}}
\end{figure}

Measuring the noise in a magnetic field sensor requires a precise
procedure and a special measurement setup. First, the magnetic field
sensor is placed in a quiet environment to minimize external
interference.

The sensor platform used here is a ready-built
\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} sensor
platform, which has been equipped with the sensors to be measured one
after the other.

The procedure begins with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of N=10000 measured values was recorded for the reference
measurement.

The output signal of the sensor is then continuously measured and
recorded. It is important to carry out the measurement over a
sufficiently long period of time in order to record both short-term and
long-term fluctuations. For this purpose, N=1000 measured values were
also taken with a trigger and readout rate of one measurement per
second.

The baseline measurement and the continuous measurement were configured
in advance using \passthrough{\lstinline!MRPCli!} \gls{cli}.

In order to quantify the noise, the standard deviation or the mean
square deviation of the signal is calculated. These parameters provide
information about the variation of the signal over time and therefore
about the sensor background noise.

After the measurements were completed, the data was evaluated using the
available MRPDataVisualization and MRPAnalysis functions. These
graphically represent the following measured values:

\begin{itemize}
\tightlist
\item
  Plot of the raw measurement data, as well as its mean value
  \passthrough{\lstinline!$\\mu\_\{rv\}$!} using Baselin
\item
  Plot of the temperature curve over the complete measurement series,
  which was recorded with the sensor's internal temperature sensor
\item
  Noise level as a percentage deviation from the baseline
\item
  Histogram of the noise level with marked standard deviation
\end{itemize}

\hypertarget{temperature-deviation}{%
\subsection{Temperature Deviation}\label{temperature-deviation}}

using same setup as in read noise but with programmed temperature
controller of the chamber

\hypertarget{linearity}{%
\subsection{Linearity}\label{linearity}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
\caption{Sensor evaluation setup for linearity measurements
\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
\end{figure}

\begin{itemize}
\tightlist
\item
  minimal distance between sensor and magnet due to messbreich
\end{itemize}

\hypertarget{result-analysis}{%
\subsubsection{Result Analysis}\label{result-analysis}}

are they suitable for \textless1000ppm ?

\begin{itemize}
\tightlist
\item
  https://onlinelibrary.wiley.com/doi/epdf/10.1002/mrm.28396
\item
  27cm / 50mT bore
\item
  nmr probes for better results
\end{itemize}

\hypertarget{software-evaluation}{%
\section{Software Evaluation}\label{software-evaluation}}

TODO: HOW TO TEST library SOFTWARE

@@

\hypertarget{hardware-preperation}{%
\subsection{Hardware preperation}\label{hardware-preperation}}

@@

\hypertarget{configuration-of-the-measurement}{%
\subsection{Configuration of the
Measurement}\label{configuration-of-the-measurement}}

@@

\hypertarget{custom-algorithm-implementation}{%
\subsection{Custom Algorithm
Implementation}\label{custom-algorithm-implementation}}

@@

\hypertarget{alternative-filter-algorithm-implementation}{%
\subsubsection{Alternative Filter Algorithm
Implementation}\label{alternative-filter-algorithm-implementation}}

@@

\hypertarget{execution-of-analysis-pipeline}{%
\subsection{Execution of Analysis
Pipeline}\label{execution-of-analysis-pipeline}}

@@

\hypertarget{result-analysis-1}{%
\subsection{Result Analysis}\label{result-analysis-1}}

@@

If the alternative filter algorithm from chapter
\passthrough{\lstinline!Alternative Filter Algorithm Implementation!}
\ref{alternative-filter-algorithm-implementation} is executed here, the
same result is returned if the magnet measurement with \gls{id}
\passthrough{\lstinline!5:0!} is used as the reference magnet.
